Resiliencia de *Quercus pyreancia* a dos eventos de sequía

### 2017-11-06 man/ms_0_intro.Rmd
update

### Sequías 
* :red_circle: Algo de las sequías de 2005 y 2014

@@

* Descripción de las sequía de 2005 y 2014

Major drought episodes in the IP were recorded in 1981, 1995, 2000 and 2005 [@VicenteSerrano2014]

La sequía es una característica del clima mediterráneo [@Lionello2012], pero en los últimos años se ha venido observando un aumento de la frecuencia y la severidad de los periodos de sequía (:red_circle: CITA;  @VicenteSerrano2014 para la P. Iberica).

The 2004/2005 and 2011/2012 hydrological years are considered two of the worst drought periods recorded in the Iberian Peninsula, particularly in the southeren sector [@GarciaHerrera2007; @Gouveia2015; @Trigo2013]. These events were extreme in both its magnitude and spatial extent [@Gouveia2014].

an increase in the drought severity in the Iberian Peninsula has been observed in the last decades [@VicenteSerrano2014].

@@

Algunos eventos extremos han aumentado su frecuencia en los últimos años

>>>>

### Sequías

Although summer drought is a characteristic feature of the Mediterranean climate [@Lionello2012], an increase in the frequency and severity of drought events have been recorded for the Mediterranean region [@Hoerling2011], particularly for southern Europe [@VicenteSerrano2014; @Spinoni2015; @Stagge2017] where a trend towards drier summers has been reported for the last three decades [@Spinoni2017b].

In the Iberian Peninsula, major drought episodies were recorded in 1981, 1995, 2000 and 2005 [@VicenteSerrano2014]. The 2004/2005 and 2011/2012 hydrological years are considered two of the worst drought periods recorded in the Iberian Peninsula, particularly in the southern sector [@GarciaHerrera2007; @Gouveia2015; @Trigo2013]. These events were extreme in both its magnitude and spatial extent [@Gouveia2014].

* :red_circle: Algo de las sequías de 2005 y 2014

@@

> notas sequia
> 
> * the drought events have been longest and most severe in the period 1991-2010 for mediterranean are of Southern Europe  
> * Seasonally, drought frequency is projected to increase everywhere in Europe for both scenarios in spring and summer, especially over southern Europe, and less intensely in autumn [@Spinoni2017a]
> Aumento de la frecuencia de sequías en spring and summer desde 1950 hasta 2014 [@Spinoni2017b]
> Both for frequency and severity, the evolution towards drier conditions is more relevant in the last three decades over Mediterranean area in summer, 
> an increase in the drought severity in the Iberian Peninsula has been observed in the last decades [@VicenteSerrano2014].

@@

### 2017-11-06 pres/state_ms.Rmd
update

---
title: "Get topographic info of gps points"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Nov"
output:  
  md_document:
    variant: markdown_github
---

```{r packages, warning=FALSE, message=FALSE}}
library("rgdal")
library("sp")
library("raster")
library("dplyr")
```

# Read data 
```{r wd, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# Connect with NAS and copy the mde file located at 
# '/cartografia/Informacion_Ambiental/BASES_DE_REFERENCIA_TERRITORIAL/MDE_SN_AreaInfluecia_10m/mde_sn_area_influencia.asc' 
#---------------------------------
```

# Extract data
```{r} 
ditemp <- paste('/Users/', machine, '/Documents/', sep='')
setwd(ditemp)

# read DEM 
demsn <- raster("mde_sn_area_influencia.asc")

setwd(di)

## Projection 
# Get projection
projection(demsn)

# Set projection
crs(demsn) <- "+proj=utm +zone=30 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

# Read points data

gps_point <- readOGR(paste0(di, 'data_raw/geoinfo/'), layer = 'dendro_garmin', verbose = FALSE)

# Read pixels data 
eviresi <- read.csv(file=paste(di, "/data/evi_resilience.csv", sep=""), header = TRUE, sep = ',')

## convert to spatial df 
eviresi_sp <- SpatialPointsDataFrame(coords = eviresi[,c('lng','lat')], data = eviresi,
                               proj4string = CRS("+init=epsg:4326"))
## reproject 
eviresi_sp <- spTransform(eviresi_sp, crs(demsn))

evi_elev <- extract(demsn, eviresi_sp, method='simple', sp=TRUE)

elev <- evi_elev@data %>% 
  dplyr::select(iv_malla_modi_id, mde_sn_area_influencia) %>%
  transmute(iv_malla_modi_id, elev = mde_sn_area_influencia)

# Export data
write.csv(elev, file=paste(di, "/data/elev.csv", sep=""), row.names = FALSE)
```
title: "Untitled"
output: html_document
---

@@

## R Markdown

>>>>

---
title: "Resiliencia de *Quercus pyreancia* a dos eventos de sequía"
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output:
  rmdshower::shower_presentation:
    self_contained: false
    katex: true
    ratio: 16x10
---

@@

## Introduccion
